---
title: "Dimension analysis"
author: "Ana Paula Chaves Steinmacher"
date: "April 4, 2019"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
library(ggplot2)
library(dplyr)
library(ggradar)
library(ggiraphExtra)

library(converse)

data('dailydialog', package = 'converse')
data('mine_to_dailydialog', package = 'converse')
data('our_updated', package = 'converse')

alldata <- rbind(dailydialog, our_updated, mine_to_dailydialog)
```

##Hypothesis

$H_0:$ Under the same interactional context, the register used by tourist assistants vs dailydialog is the same.

##Start by analyzing the dimensions

```{r echo=FALSE}
dd_flg <- alldata %>% filter(source != "translation")
dd_flg_mod <- alldata %>% filter(source != "our")
```

Descriptive statistics:

```{r echo=FALSE}
#Descriptive statistics

stats <- data.frame(alldata %>% 
  group_by(source) %>%
  summarise(mean_dim1 = mean(dim_1),
            sd_dim1 = sd(dim_1),
            mean_dim2 = mean(dim_2),
            sd_dim2 = sd(dim_2),
            mean_dim3 = mean(dim_3),
            sd_dim3 = sd(dim_3),
            mean_dim4 = mean(dim_4),
            sd_dim4 = sd(dim_4),
            mean_dim5 = mean(dim_5),
            sd_dim5 = sd(dim_5),
            ))

stats
```

## Plotting the dimensions
```{r warning=FALSE, error=FALSE, message=FALSE, echo=FALSE}
#per source
dim_radar_mean_guide <- data.frame(group = c("dailydialog", "FLG", "FLG_mod"),
                                     dim_1 = c(stats$mean_dim1),
                                     dim_2 = c(stats$mean_dim2),
                                     dim_3 = c(stats$mean_dim3),
                                     dim_4 = c(stats$mean_dim4),
                                     dim_5 = c(stats$mean_dim5))
g <- ggRadar(data=dim_radar_mean_guide, aes(color=group)) +  ggtitle("Mean - Tour Guide")
#ggsave(g, file="plot.png")
```


## Multivariate analysis

```{r}
#Model that compares DailyDialog to FLG (orignal data)
fit <- manova(cbind(dim_1, dim_2, dim_3, dim_4, dim_5) ~ source, data = dd_flg)
summary(fit, test = "Wilks")
summary.aov(fit)

#Model that compares DailyDialog to FLG_mod (modified data)
fit <- manova(cbind(dim_1, dim_2, dim_3, dim_4, dim_5) ~ source, data = dd_flg_mod)
summary(fit, test = "Wilks")
summary.aov(fit)
```

## Confirm the inference with permutation manova

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
#dimension analysis of DailyDialog vs. FLG
dim <- dd_flg %>% select(individual, source, dim_1, dim_2, dim_3, dim_4, dim_5)

library(vegan)

set.seed(36) #reproducible results

dim.div <- adonis(dim[,3:7]~source, data=dd_flg, method="euclidean", permutations = 10000)
dim.div$aov.tab

#dimension analysis of DailyDialog vs. FLG
dim <- dd_flg_mod %>% select(individual, source, dim_1, dim_2, dim_3, dim_4, dim_5)

dim.div <- adonis(dim[,3:7]~source, data=dd_flg_mod, method="euclidean", permutations = 10000)
dim.div$aov.tab
```

## Dimension 1 - ANOVA

```{r echo=FALSE}
dim_1.model <- lm(dim_1~source, data=dd_flg)
summary(dim_1.model)

dim_1.model <- lm(dim_1~source, data=dd_flg_mod)
summary(dim_1.model)
```

## Dimension 2 - ANOVA

```{r echo=FALSE}
dim_2.model <- lm(dim_2~source, data=dd_flg)
summary(dim_2.model)

dim_2.model <- lm(dim_2~source, data=dd_flg_mod)
summary(dim_2.model)
```

## Dimension 3 - ANOVA

```{r echo=FALSE}
dim_3.model <- lm(dim_3~source, data=dd_flg)
summary(dim_1.model)

dim_3.model <- lm(dim_3~source, data=dd_flg_mod)
summary(dim_3.model)
```

## Dimension 4 - ANOVA

```{r echo=FALSE}
dim_4.model <- lm(dim_4~source, data=dd_flg)
summary(dim_4.model)

dim_4.model <- lm(dim_4~source, data=dd_flg_mod)
summary(dim_4.model)
```

## Dimension 5 - ANOVA

```{r echo=FALSE}
dim_5.model <- lm(dim_5~source, data=dd_flg)
summary(dim_5.model)

dim_5.model <- lm(dim_5~source, data=dd_flg_mod)
summary(dim_5.model)
```