---
title: "DailyDialog Transfer-Sentence Vallidation"
author: "Ana Paula Chaves Steinmacher"
date: "2/12/2020"
output:
  word_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r loadingData, echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(surveystats)
library(ggplot2)
library(rcompanion) #for groupwisePercentile() function
library(lme4) #for mixed effect model lmer()
library(lmerTest) #interface for lme4 that shows the pvalues
library(latex2exp)  # for LaTeX mathematical notation

data("content.preservation")
data("naturalness")
```

# Content Preservation

```{r content, echo=FALSE}
#calculating the .25 lower quantile
grp.quantile <- groupwisePercentile(score ~ question, bca=FALSE, tau=.25, data = content.preservation)
grp.quantile <- grp.quantile %>%
  select(question, Percentile)

#density plot with cutting line
ggplot(content.preservation, aes(x = score))+
  geom_density(show.legend = FALSE)+
  facet_wrap(question~.,ncol = 9)+
  geom_vline(data=grp.quantile, aes(xintercept=Percentile), #percentile line is blue (should be to the right)
             colour="blue", show.legend = FALSE)+ 
  geom_vline(aes(xintercept=75),                            #cut off line is red
             colour="tomato", linetype="dashed", show.legend = FALSE)+
      theme_bw()+theme(panel.spacing=grid::unit(0, "lines"))
```

##Some statistics

H0: $$\mu = 75$$ ; Ha: $$\mu < 75$$

We fitted a model with the score as response variable and no fixed effect, we only care about the intercept (the 1 in the model). To support H0, the intercept must be above 75, and 75 must not be within the confidence interval. The model also has two random effects: the questions and the participants.

```{r}
model <- lmer(score ~ 1 + (1|question) + (1|pid), data=content.preservation)
summary(model)
#estimates for question and pid
#ranef(model)

#random effects
ranova(model)
LetterResults <- emmeans::emmeans( model, ~ 1) %>%
  multcomp::cld(Letters=letters)
```

The model shows that the estimated value for similarity is `r summary(model)$coef[1]` with confidence intervals (`r LetterResults$lower.CL`, `r LetterResults$upper.CL`), which is a good similarity rate. The BLEU score for Machine Translated data is 51.45 (calculated from https://www.letsmt.eu/Bleu.aspx), which is above the threshold for good, fluent translations (citation: wolk2015neural).

The random effects show that the variability is mostly explained by the participants, rather than the pure error (residual).

```{r}
cp.plot <- content.preservation %>%
  mutate( y.hat.question   = predict(model, re.form= ~ (1|question)),  # Include question Random effect
          y.hat.question   = round( y.hat.question, digits=2),
          y.hat.pid        = predict(model, re.form= ~ (1|pid)),  # Include pid Random effect
          y.hat.pid        = round( y.hat.pid, digits=2),)

#creating the plot por every question
ggplot(cp.plot, aes(y = score, x=question)) +
  geom_point() +
  theme(legend.position="top",
        legend.text = element_text(size=4),
        legend.title = element_blank(),
        legend.key.size = unit(.4,"line")) +
  guides(col = guide_legend(ncol = 8)) + #this line is not working
  geom_hline(aes(yintercept=y.hat.pid),                            #random effect of pid is red
             color="tomato", linetype="dashed", show.legend = FALSE) +
  facet_wrap(. ~ pid, ncol = 14, labeller = label_both) +
  geom_hline(aes(yintercept=y.hat.question),                            #random effect of pid is blue
             color="blue", linetype="dashed", show.legend = FALSE)
```

#Naturalness

```{r naturalness, echo=FALSE}
#boxplot with all the items per question, separate into original vs. modified
ggplot(naturalness, aes(y=score, x=item, fill=group))+
  facet_wrap(. ~ question, ncol=10)+
  geom_boxplot()+ theme(legend.position="top")
```

## Descriptive Stats

### Turning scores into an ordinal factor

Score (reduced) is the aggregation of the Likert-scale responses from 1-7 into three groups, namely, negative answers (1-3), neutral answer (4), and positive answers (5-7).

```{r, message=FALSE, warning=FALSE}
#overall stats
summary(naturalness)

library(psych)
xt <- xtabs(~ group + score.reduced, data=naturalness)
xt

```

###Median for the questions (ignoring items)
```{r descstas, echo=FALSE, warning=FALSE, message=FALSE}
desc.stats <- naturalness %>%
  filter(group == "original") %>%
  group_by(question) %>%
  summarise(med.o = median(score))

desc.stats <- cbind(desc.stats, naturalness %>%
    filter(group == "translated") %>%
    group_by(question) %>%
    summarise(med.t = median(score)) %>%
    select(med.t))

desc.stats <- desc.stats %>%
  mutate(diff = med.o-med.t)

desc.stats

#Barplot of differences between medians per question
barplot(desc.stats$diff,
        col="dark gray",
        xlab="Observation",
        ylab="Difference (Median Original – Median Modified)")
```

## Some statistics
```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(ordinal)
library(car)
library(RVAideMemoire)
library(emmeans)

nat <- naturalness %>%
  filter(item=="natural") %>%
  select(-item)

well.wr <- naturalness %>%
  filter(item=="well.written") %>%
  select(-item)

meaning <- naturalness %>%
  filter(item=="meaningful") %>%
  select(-item)

complete <- naturalness %>%
  filter(item=="complete") %>%
  select(-item)

model.nat <- clmm(score.reduced ~ group + (1|group:question) + (1|pid),
            data = nat)
summary(model.nat)

model.well.wr <- clmm(score.reduced ~ group + (1|group:question) + (1|pid),
            data = well.wr)
summary(model.well.wr)

model.meaning <- clmm(score.reduced ~ group + (1|group:question) + (1|pid),
            data = meaning)
summary(model.meaning)

model.complete <- clmm(score.reduced ~ group + (1|group:question) + (1|pid),
            data = complete)
summary(model.complete)
```
